New lower bounds for Schur and weak Schur numbers

### 2021-10-06 article/article.tex
affiliations modifiees

\address[1]{\textit{CentraleSup\'elec}, Universit\'e Paris-Saclay}
\address[2]{LRI, \textit{CentraleSup\'elec}, Universit\'e Paris-Saclay, F-91405, Orsay, France}

@@

First we would like to thank our school \textit{CentraleSupélec} and its pole "Formation \`a la recherche" which allowed us to work
on this project during our studies. We also would like to address warm thanks to Fred Rowley who kindly answered our many questions
and with who it was a pleasure to exchange. Last but not least, we would like to thank Marijn Heule for providing the backdoors
used in the computation of the new lower bound for \(\WS(6)\).

>>>>

\address[1]{CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 190 Gif-sur-Yvette, France}
\address[2]{LISN, CentraleSup\'elec, Universit\'e{} Paris-Saclay, 91 405, Orsay, France}

@@

This study results from a long-term project performed within the framework of the Project Cluster "Training for Research" of CentraleSupélec. 
We would like to address warm thanks to Fred Rowley who kindly answered our many questions
and with who it was a pleasure to exchange. Last but not least, we would like to thank Marijn Heule for providing the backdoors
used in the computation of the new lower bound for \(\WS(6)\).
